Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Paris version \YellowPaperVersionNumber}}

### 2024-06-26 Paper.tex
Fix returndata details (#909)
* Fix returndata details

* Replace 'cache' with 'buffer'

* Reorder tuple elements

* Rename 'cache' to 'buffer', revert some changes

\subsubsection{Machine State}
The machine state $\boldsymbol{\mu}$ is defined as the tuple $(g, pc, \mathbf{m}, i, \mathbf{s}, \mathbf{o})$ which are the gas available, the program counter $pc \in \mathbb{N}_{256}$ , the memory contents, the active number of words in memory (counting continuously from position 0), the stack contents, and the returndata cache. The memory contents $\boldsymbol{\mu}_{\mathbf{m}}$ are a series of zeroes of size $2^{256}$.

@@

\begin{tabu}{\usetabu{opcodes}}
\midrule
0x3d & {\small RETURNDATASIZE} & 0 & 1 & Get size of output data from the previous call from the current\\
&&&& environment. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv \lVert \boldsymbol{\mu}_{\mathbf{o}} \rVert$ \\
\midrule
0x3e & {\small RETURNDATACOPY} & 3 & 0 & Copy output data from the previous call to memory. \\
&&&& reverts if $\quad \boldsymbol{\mu}_{\mathbf{s}}[1] + \boldsymbol{\mu}_{\mathbf{s}}[2] > \lVert\boldsymbol{\mu}_{\mathbf{o}}\rVert$\\
&&&& $\forall i \in \{ 0 \dots \boldsymbol{\mu}_{\mathbf{s}}[2] - 1\}: \boldsymbol{\mu}'_{\mathbf{m}}[\boldsymbol{\mu}_{\mathbf{s}}[0] + i ] \equiv
\boldsymbol{\mu}_{\mathbf{o}}[\boldsymbol{\mu}_{\mathbf{s}}[1] + i]$\\
&&&& The additions in $\boldsymbol{\mu}_{\mathbf{s}}[1] + i$ are not subject to the $2^{256}$ modulo. \\
&&&& $\boldsymbol{\mu}'_{\mathrm{i}} \equiv M(\boldsymbol{\mu}_{\mathrm{i}}, \boldsymbol{\mu}_{\mathbf{s}}[0], \boldsymbol{\mu}_{\mathbf{s}}[2])$ \\
\midrule
\linkdest{extcodehash}{}0x3f & {\small EXTCODEHASH} & 1 & 1 & Get hash of an account's code. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv
\begin{cases} 0 & \text{if} \quad \mathtt{DEAD}(\boldsymbol{\sigma}, \boldsymbol{\mu}_{\mathbf{s}}[0] \bmod 2^{160}) \\ \boldsymbol{\sigma}[\boldsymbol{\mu}_{\mathbf{s}}[0] \bmod 2^{160}]_{\mathrm{c}} & \text{otherwise} \end{cases}$ \\
&&&& $A'_{\mathbf{a}} \equiv A_{\mathbf{a}} \cup \{ \boldsymbol{\mu}_{\mathbf{s}}[0] \bmod 2^{160} \}$ \\
\bottomrule
\end{tabu}

>>>>

\subsubsection{Machine State}
The machine state $\boldsymbol{\mu}$ is defined as the tuple $(g, pc, \mathbf{m}, i, \mathbf{s}, \mathbf{o})$ which are the gas available, the program counter $pc \in \mathbb{N}_{256}$ , the memory contents, the active number of words in memory (counting continuously from position 0), the stack contents, and the returndata buffer. The memory contents $\boldsymbol{\mu}_{\mathbf{m}}$ are a series of zeroes of size $2^{256}$.

@@

\begin{tabu}{\usetabu{opcodes}}
\midrule
0x3d & {\small RETURNDATASIZE} & 0 & 1 & Get size of output data from the previous call from the current\\
&&&& environment. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv \lVert \boldsymbol{\mu}_{\mathbf{o}} \rVert$ \\
\midrule
0x3e & {\small RETURNDATACOPY} & 3 & 0 & Copy output data from the previous call to memory. \\
&&&& $\forall i \in \{ 0 \dots \boldsymbol{\mu}_{\mathbf{s}}[2] - 1\}: \boldsymbol{\mu}'_{\mathbf{m}}[\boldsymbol{\mu}_{\mathbf{s}}[0] + i ] \equiv
\begin{cases} \boldsymbol{\mu}_{\mathbf{o}}[\boldsymbol{\mu}_{\mathbf{s}}[1] + i] & \text{if} \quad \boldsymbol{\mu}_{\mathbf{s}}[1] + i < \lVert \boldsymbol{\mu}_{\mathbf{o}} \rVert \\ 0 & \text{otherwise} \end{cases}$\\
&&&& The additions in $\boldsymbol{\mu}_{\mathbf{s}}[1] + i$ are not subject to the $2^{256}$ modulo. \\
&&&& $\boldsymbol{\mu}'_{\mathrm{i}} \equiv M(\boldsymbol{\mu}_{\mathrm{i}}, \boldsymbol{\mu}_{\mathbf{s}}[0], \boldsymbol{\mu}_{\mathbf{s}}[2])$ \\
\midrule
\linkdest{extcodehash}{}0x3f & {\small EXTCODEHASH} & 1 & 1 & Get hash of an account's code. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv
\begin{cases} 0 & \text{if} \quad \mathtt{DEAD}(\boldsymbol{\sigma}, \boldsymbol{\mu}_{\mathbf{s}}[0] \bmod 2^{160}) \\ \boldsymbol{\sigma}[\boldsymbol{\mu}_{\mathbf{s}}[0] \bmod 2^{160}]_{\mathrm{c}} & \text{otherwise} \end{cases}$ \\
&&&& $A'_{\mathbf{a}} \equiv A_{\mathbf{a}} \cup \{ \boldsymbol{\mu}_{\mathbf{s}}[0] \bmod 2^{160} \}$ \\
\bottomrule
\end{tabu}
